Simple repression draft

### 2020-05-27 doc/section_03_beyond_means.tex
update caption

\begin{figure}%[h!]
\centering
\includegraphics[width=\textwidth]{../figures/main/fig02.pdf}
\caption{\textbf{Comparison of different models for noise in the constitutive promoter.}
The left column depicts various plausible models for the dynamics of
constitutive promoters. In model (1), transcripts are produced in a Poisson
process~\cite{Sanchez2013, Jones2014}. Model (2) features explicit modeling of
RNAP binding/unbinding kinetics~\cite{Phillips2015a}. Model (3) is a more
detailed generalization of model (2), treating transcription initiation as a
multi-step process proceeding through closed and open
complexes~\cite{Mitarai2015}. Model (4) is somewhat analogous to (2) except with
the precise nature of active and inactive states left
ambiguous~\cite{Peccoud1995, Shahrezaei2008, Razo-Mejia2020}. Finally, model (5)
can be viewed as a certain limit of model (4) in which transcripts are produced
in bursts, and initiation of bursts is a Poisson process. 
% \mmnote{Haven't found model 5 formulated quite like this in the literature,
% usually burstiness is handled like model 4, but I should probably search a bit
% more.} 
The right column shows the Fano factor $\nu$ (variance/mean) for each model.
Note especially the crucial diagnostic: (2) and (3) have $\nu$ strictly below 1,
while only for (4) and (5) can $\nu$ exceed 1. Models with Fano factors $\le 1$
cannot produce the FISH data observed in~\cite{Jones2014} without introducing
additional assumptions and model complexity.}
\label{fig2:constit_cartoons}
\end{figure}

>>>>

\begin{figure}%[h!]
\centering
\includegraphics[width=\textwidth]{../figures/main/fig02.pdf}
\caption{\textbf{Comparison of different models for noise in the constitutive promoter.}
(A) The left column depicts various plausible models for the dynamics of
constitutive promoters. In model (1), transcripts are produced in a Poisson
process~\cite{Sanchez2013, Jones2014}. Model (2) features explicit modeling of
RNAP binding/unbinding kinetics~\cite{Phillips2015a}. Model (3) is a more
detailed generalization of model (2), treating transcription initiation as a
multi-step process proceeding through closed and open
complexes~\cite{Mitarai2015}. Model (4) is somewhat analogous to (2) except with
the precise nature of active and inactive states left
ambiguous~\cite{Peccoud1995, Shahrezaei2008, Razo-Mejia2020}. Finally, model (5)
can be viewed as a certain limit of model (4) in which transcripts are produced
in bursts, and initiation of bursts is a Poisson process. 
% \mmnote{Haven't found model 5 formulated quite like this in the literature,
% usually burstiness is handled like model 4, but I should probably search a bit
% more.} 
The right column shows the Fano factor $\nu$ (variance/mean) for each model.
Note especially the crucial diagnostic: (2) and (3) have $\nu$ strictly below 1,
while only for (4) and (5) can $\nu$ exceed 1. Models with Fano factors $\le 1$
cannot produce the FISH data observed in part (B) without introducing
additional assumptions and model complexity. (B) Data from \cite{Jones2014}.
Mean mRNA count vs. Fano factor (variance/mean) for different promoters as
determined with single-molecule mRNA FISH. The colorbar indicates the predicted
binding affinity of RNAP to the promoter sequence as determined in
\cite{Brewster2012}. Numbers serve for cross comparison with data presented in 
Figure 3.}
\label{fig2:constit_cartoons}
\end{figure}
